Macro Impacts

### 2016-07-09 Macro Impacts Revised.tex
Oh man, I hope this is correct

\Xi&\leq\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

@@

>>>>

\Xi&<\p{\f{K^2}{\lambda+2\mu}}\p{\f{3\pi}{2\bar p\lambda_0}}^2\abs{\td{E}{x}{}}\,.

@@

Note the strict inequality: $\Delta r=0$ corresponds to $r_0=\infty$.

@@

\section{P-Wave Vector Propagation}
Observe, by Snell's law, we have that
p=\f{r\sin\theta}{v}\,,
is constant along any fixed ray, and is given by the above form in a spherically symmetric velocity field. $\theta$ is the angle of incidence, $r$ is the distance from the origin, and $v$ is the velocity at radius $r$. Let $\sigma(s)$ be the parametrized curve followed by a p-wave. Then
\cos\theta=\f{\hat r\cdot\dot\sigma(s)}{\|\sigma(s)\|}=\f{\sigma(s)\cdot\dot\sigma(s)}{\|\sigma(s)\|\|\dot\sigma(s)\|}\,.
From this we obtain
\p{\f{pv}{r}}^2=1-\f{(\sigma\cdot\dot\sigma)^2}{(\|\sigma(s)\|\|\dot\sigma(s)\|)^2}\,,
If we denote the radial component as $r(s)$ and the angular component $\theta(s)$ we obtain the differential equation
\p{\f{pv}{r}}^2=\f{r^2\dot \theta^2}{(\dot r^2+\dot\theta^2 r^2)}\,.
But observe, the velocity of the curve $\sigma$ is just the velocity in the medium, hence
\p{\f{pv}{r}}^2=r^2\f{\dot \theta^2}{v^2}\,,
from which we obtain the equation for $\theta$,
\dot \theta&=\f{p v^2}{r^2}
We now use the velocity definition to obtain an implicit equation for $r$. Observe
v^2&=\dot r^2+\dot\theta^2r^2\,,\\
&=\dot r^2+\f{p^2 v^4}{r^2}\,,
hence
1&=\f{r\dot r}{\sqrt{v^2r^2-p^2v^4}}
This can be integrated directly, yielding
s+C&=\int\f{r\diff r}{\sqrt{v^2r^2-p^2v^4}}\,.
In the case that $v$ is a power law, i.e.
v(r)&=v_0\p{\f{r_0}{r}}^\alpha
we can directly integrate for integer $\alpha$, yielding
s+C&=\f{r^{2\alpha}r_0^{-2\alpha}\sqrt{r^{-4\alpha}r_0^{2\alpha}v_0^2(r^{2+2\alpha}-p^2r_0^{2\alpha}v_0^2)}}{v_0^2(1+\alpha)}\,.
It is possible to invert this equation for any particular $\alpha$. One solution which holds for all $\alpha$ is
r(s)&=r_0^{\f{\alpha}{1+\alpha}}v_0^{\f{1}{1+\alpha}}(p^2+(C+s)^2(1+\alpha)^2)^{\f{1}{2(1+\alpha)}}\,.
We thus obtain the following expression for $\theta$:
\theta(s)&=\f{1}{1+\alpha}\arctan\ps{\f{1+\alpha}{p}(C+s)}+\theta_0
WOAH!
